---
title: "Robust Design AsMi"
author: "Michelle DePrenger-Levin"
date: "2023-11-30"
output: ''
---

compare multi-state mark-recapture to MPM estimates of survival, transitions


Libraries and data
```{r}
rm(list=ls())
library(dplyr)
library(tidyr)
library(ggplot2)
library(RMark)
library(popbio)
library(RCurl)
library(devtools)
library(HDInterval)
library(Rage)

load("data/asmiRD.Rdata")
load("data/plotdf.Rdata")
load("data/sitedf.Rdata")

```


## Compare to 3 stage for just the years 2013-2015 and grouping by site  
```{r}
## Get 3 stage pva to make MPMs; token is updated, need to copy current token to source. 
source_url("https://raw.githubusercontent.com/DenverBotanicGardens/DormancyDetection/main/StagePVA3stages.R")

load("data/asmi.all2.Rdata")

asmi.allSite <- asmi.all2 %>%
  filter(site %in% c(5,15,19,26)) %>%
  filter(year > 2012 & year < 2016) %>%
  mutate(plot = site)

table(asmi.allSite$plot, asmi.allSite$site)

## StagePVA3stages.R
MPM.plots <- StagePVA(asmi.allSite,TF = FALSE)
MPM.plotsSplit <- StagePVA(asmi.allSite,TF = TRUE)

### Three years at four sites
asmi.3yrs <- asmi.all2 %>%
  filter(site %in% c(5,15,19,26)) %>%
  filter(year > 2012 & year < 2016) %>%
  StagePVA(TF = TRUE)


```



instead of dot notation (robust models and pradel won't accept "." for missing surveys even though Cooch and Laake say they do!!), fix the probabilities of detection to zero for those periods in the ddls. fix p=0 for that occasion.      
```{r}

## dataCJS
load("data/dataCJS3yrs.Rdata")

## Can only be one strata within a primary session - need to assign V if never reproductive, R if eventually reproductive  
##### Could condense to spring and fall, then have V early and some R late
## Repeated for the three years
obsmodel <- dataCJS %>%
  filter(Site %in% c(5,15,19,26)) %>%
  group_by(Year, Plot, Site, Tag) %>%
  ## Make the multistate options
  dplyr::mutate(MSObs = case_when(Ln == 0 ~ "0",
                                  (Ln > 0 & Fl == 0) ~ "V",
                                  any((Ln > 0 & Fl == 1)) ~ "R")) %>%
  # dplyr::mutate(MSObs = case_when(any(MSObs == "R") ~ replace(MSObs, MSObs == "V", "R"),
  #                                 TRUE ~ MSObs)) %>%
  ungroup()%>%
  distinct(Day,Year,Plot,Site,Tag,encounter, .keep_all = TRUE) %>%
  # dplyr::select(c(Site:Tag, encounter, Obs, Year)) %>%
  dplyr::select(c(Site:Tag, encounter, MSObs, Year)) %>%
  ## Fill in all tags within a Plot and Site across all years
  tidyr::complete(nesting(Site,Plot,Tag),Year, encounter, fill = list(MSObs = "0")) %>%
  arrange(encounter) %>%
  pivot_wider(names_from = encounter, values_from = MSObs, values_fill = "0", names_prefix = "Occ") 

obsmodel %>%
  filter(if_any(.cols = everything(), ~ grepl("V", .))) %>%
  print(n=100)

dataCJS <- dataCJS %>% filter(Site %in% c(5,15,19,26))
plotssurveyed <- table(dataCJS$Plot, dataCJS$encounter, dataCJS$Year)  

## In the design data lists after processing data, set these to zero detection (p)


asmiRD <- obsmodel %>%
  ## unite within each year
  tidyr::unite(ch, Occ1:Occ10, sep="") %>%
  ## Change all to R if any within a year
  dplyr::mutate(ch = if_else(grepl("R",ch), gsub("V","R",ch), ch)) %>%
  dplyr::group_by(Site,Plot,Tag) %>%
  dplyr::mutate(Plot = as.factor(Plot)) %>%
  dplyr::mutate(Site = as.factor(Site)) %>%
  ## paste across years
  dplyr::summarise(ch = paste0(ch, collapse = "")) %>%
  ungroup() %>%
  filter((grepl("V", ch) | grepl("R",ch)))

asmiRD %>%
  filter(grepl("R",ch))

dmPlot <- model.matrix(~ -1 + Plot, asmiRD)
dmSite <- model.matrix(~ -1 + Site, asmiRD)
dimnames(dmPlot)[[2]][length(dimnames(dmPlot)[[2]])]
dimnames(dmSite)[[2]][length(dimnames(dmSite)[[2]])]

## By Plot
asmiRD %>%
  ungroup() %>%
  dplyr::select(c(ch)) %>%
  bind_cols(dmPlot) %>%
  mutate(Plot614 = paste(Plot614, ";", sep ="")) %>%
  write.table(file = "data/Robust3yearsPlot.inp", 
              sep = " ", col.names = FALSE, row.names = FALSE)

## By Site
asmiRD %>%
  ungroup() %>%
  dplyr::select(c(ch)) %>%
  bind_cols(dmSite) %>%
  mutate(Site26 = paste(Site26, ";", sep ="")) %>%
  write.table(file = "data/Robust3yearsSite.inp", 
              sep = " ", col.names = FALSE, row.names = FALSE)


```



Mark-recapture by plot  
Mark-recpature by site
```{r}



plotdf <- asmiRD %>%
  ungroup()%>%
  dplyr::distinct(Plot)

sitedf <- asmiRD %>%
  ungroup() %>%
  dplyr::distinct(Site)


## Convert for MARK  
asmiRDPlot.inp <- convert.inp("data/Robust3yearsPlot.inp", 
                        group.df = plotdf,
                        covariates = NULL,
                        use.comments = FALSE)

asmiRDSite.inp <- convert.inp("data/Robust3yearsSite.inp", 
                        group.df = sitedf,
                        covariates = NULL,
                        use.comments = FALSE)
```


In the dll PIMs set p and c to zero for all times not surveyed   

# Huggins Closed Robust Design Multi-state with State Probabilities  
"CRDMSOHug"


We used a Robust design with a Huggins’ estimator in Program MARK (accessed through RMark ) to estimate survival and a Pradel Robust Model with survival and Lambda with Huggins’ closed capture estimator in Program MARK to estimate the population growth rate (Pollock, 1982; White et al., 2001). 


S(s): survival rate between primary occasions for state s 
Psi(r,s): transition between states between primary periods from r to state s
Omega: probability of being in each of the states
p(s,t): apparent detection
c(s,t): true detection   
```{r}

time.intervals <- c(0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0,1,0,0,0,0,0,0,0,0,0) 

RDproc <- process.data(asmiRDPlot.inp, model = "CRDMSOHug", begin.time = 2013, groups = "Plot",
                       time.intervals = time.intervals)
RDddl <- make.design.data(RDproc) #, parameters = list(Psi = list(subtract.stratum = c("R","R"))))

RDddl$Psi$stratum <- factor(RDddl$Psi$stratum, levels = c("R","V"))
RDddl$S$stratum <- factor(RDddl$S$stratum, levels = c("R","V"))
RDddl$Omega$stratum <- factor(RDddl$Omega$stratum, levels = c("R","V"))
RDddl$p$stratum <- factor(RDddl$p$stratum, levels = c("R","V"))
RDddl$c$stratum <- factor(RDddl$c$stratum, levels = c("R","V"))

table(RDddl$Psi[,c("stratum","tostratum")]) ## R to R and V to V computed by subtraction
## Now add zero for detection p, at all times when not visited; session = Year, time = secondary occasion 1:10, Plot = Plot
pindex <- RDddl$p
## Missed entire survey period
p2013.indices <- pindex %>%
  filter(session == 2013 & time %in% c(1,2,4,5,7,9))
## Missed these plots [Plot, Survey, Year]
p2013.ind3 <- pindex %>%
  filter(session == 2013 & time == 3 & Plot %in% as.numeric(names(plotssurveyed[,3,1])[which(plotssurveyed[,3,1] == 0)]))
p2013.ind6 <- pindex %>%
  filter(session == 2013 & time == 6 & Plot %in% as.numeric(names(plotssurveyed[,6,1])[which(plotssurveyed[,6,1] == 0)])) 
p2013.ind8 <- pindex %>%
  filter(session == 2013 & time == 8 & Plot %in% as.numeric(names(plotssurveyed[,8,1])[which(plotssurveyed[,8,1] == 0)])) 
p2013.ind10 <- pindex %>%
  filter(session == 2013 & time == 10 & Plot %in% as.numeric(names(plotssurveyed[,10,1])[which(plotssurveyed[,10,1] == 0)])) 
p2013.inds <- c(p2013.indices$par.index, p2013.ind3$par.index, p2013.ind6$par.index, p2013.ind8$par.index, p2013.ind10$par.index)

## Missed in 2014
p2014.indices <- pindex %>%
  filter(session == 2014 & time == 4)
p2014.ind1 <- pindex %>%
  filter(session == 2014 & time == 1 & Plot %in% as.numeric(names(plotssurveyed[,1,2])[which(plotssurveyed[,1,2] == 0)])) 
p2014.ind2 <- pindex %>%
  filter(session == 2014 & time == 2 & Plot %in% as.numeric(names(plotssurveyed[,2,2])[which(plotssurveyed[,2,2] == 0)])) 
p2014.ind3 <- pindex %>%
  filter(session == 2014 & time == 3 & Plot %in% as.numeric(names(plotssurveyed[,3,2])[which(plotssurveyed[,3,2] == 0)])) 
p2014.ind5 <- pindex %>%
  filter(session == 2014 & time == 5 & Plot %in% as.numeric(names(plotssurveyed[,5,2])[which(plotssurveyed[,5,2] == 0)]))
p2014.ind6 <- pindex %>%
  filter(session == 2014 & time == 6 & Plot %in% as.numeric(names(plotssurveyed[,6,2])[which(plotssurveyed[,6,2] == 0)])) 
p2014.ind7 <- pindex %>%
  filter(session == 2014 & time == 7 & Plot %in% as.numeric(names(plotssurveyed[,7,2])[which(plotssurveyed[,7,2] == 0)])) 
p2014.ind8 <- pindex %>%
  filter(session == 2014 & time == 8 & Plot %in% as.numeric(names(plotssurveyed[,8,2])[which(plotssurveyed[,8,2] == 0)])) 
p2014.ind9 <- pindex %>%
  filter(session == 2014 & time == 9 & Plot %in% as.numeric(names(plotssurveyed[,9,2])[which(plotssurveyed[,9,2] == 0)])) 
p2014.ind10 <- pindex %>%
  filter(session == 2014 & time == 10 & Plot %in% as.numeric(names(plotssurveyed[,10,2])[which(plotssurveyed[,10,2] == 0)])) 
p2014.inds <- c(p2014.indices$par.index, p2014.ind1$par.index, p2014.ind2$par.index, p2014.ind3$par.index, p2014.ind5$par.index,
                p2014.ind6$par.index, p2014.ind7$par.index, p2014.ind8$par.index, p2014.ind9$par.index, p2014.ind10$par.index)

## Missed in 2015
p2015.indices <- pindex %>%
  filter(session == 2015 & time == 10) 
p2015.ind1 <- pindex %>%
  filter(session == 2015 & time == 1 & Plot %in% as.numeric(names(plotssurveyed[,1,3])[which(plotssurveyed[,1,3] == 0)])) 
p2015.ind2 <- pindex %>%
  filter(session == 2015 & time == 2 & Plot %in% as.numeric(names(plotssurveyed[,2,3])[which(plotssurveyed[,2,3] == 0)])) 
p2015.ind3 <- pindex %>%
  filter(session == 2015 & time == 3 & Plot %in% as.numeric(names(plotssurveyed[,3,3])[which(plotssurveyed[,3,3] == 0)]))
p2015.ind4 <- pindex %>%
  filter(session == 2015 & time == 4 & Plot %in% as.numeric(names(plotssurveyed[,4,3])[which(plotssurveyed[,4,3] == 0)]))
p2015.ind5 <- pindex %>%
  filter(session == 2015 & time == 5 & Plot %in% as.numeric(names(plotssurveyed[,5,3])[which(plotssurveyed[,5,3] == 0)])) 
p2015.ind6 <- pindex %>%
  filter(session == 2015 & time == 6 & Plot %in% as.numeric(names(plotssurveyed[,6,3])[which(plotssurveyed[,6,3] == 0)])) 
p2015.ind7 <- pindex %>%
  filter(session == 2015 & time == 7 & Plot %in% as.numeric(names(plotssurveyed[,7,3])[which(plotssurveyed[,7,3] == 0)])) 
p2015.ind8 <- pindex %>%
  filter(session == 2015 & time == 8 & Plot %in% as.numeric(names(plotssurveyed[,8,3])[which(plotssurveyed[,8,3] == 0)])) 
p2015.ind9 <- pindex %>%
  filter(session == 2015 & time == 9 & Plot %in% as.numeric(names(plotssurveyed[,9,3])[which(plotssurveyed[,9,3] == 0)])) 

p2015.inds <- c(p2015.indices$par.index, p2015.ind1$par.index, p2015.ind2$par.index, p2015.ind3$par.index, p2015.ind4$par.index,
                p2015.ind5$par.index, p2015.ind6$par.index, p2015.ind7$par.index, p2015.ind8$par.index, p2015.ind9$par.index)


## Final for all missed ones that need to be zero
p.indices <- c(p2013.inds,p2014.inds, p2015.inds)
p.values <- rep(0, length(p.indices))

############################### c indeces
cindex <- RDddl$c
## Missed entire survey period
c2013.indices <- cindex %>%
  filter(session == 2013 & time %in% c(1,2,4,5,7,9))
## Missed these plots [Plot, Survey, Year]
c2013.ind3 <- cindex %>%
  filter(session == 2013 & time == 3 & Plot %in% as.numeric(names(plotssurveyed[,3,1])[which(plotssurveyed[,3,1] == 0)]))
c2013.ind6 <- cindex %>%
  filter(session == 2013 & time == 6 & Plot %in% as.numeric(names(plotssurveyed[,6,1])[which(plotssurveyed[,6,1] == 0)])) 
c2013.ind8 <- cindex %>%
  filter(session == 2013 & time == 8 & Plot %in% as.numeric(names(plotssurveyed[,8,1])[which(plotssurveyed[,8,1] == 0)])) 
c2013.ind10 <- cindex %>%
  filter(session == 2013 & time == 10 & Plot %in% as.numeric(names(plotssurveyed[,10,1])[which(plotssurveyed[,10,1] == 0)])) 
c2013.inds <- c(c2013.indices$par.index, c2013.ind3$par.index, c2013.ind6$par.index, c2013.ind8$par.index, c2013.ind10$par.index)

## Missed in 2014
c2014.indices <- cindex %>%
  filter(session == 2014 & time == 4)
c2014.ind1 <- cindex %>%
  filter(session == 2014 & time == 1 & Plot %in% as.numeric(names(plotssurveyed[,1,2])[which(plotssurveyed[,1,2] == 0)])) 
c2014.ind2 <- cindex %>%
  filter(session == 2014 & time == 2 & Plot %in% as.numeric(names(plotssurveyed[,2,2])[which(plotssurveyed[,2,2] == 0)])) 
c2014.ind3 <- cindex %>%
  filter(session == 2014 & time == 3 & Plot %in% as.numeric(names(plotssurveyed[,3,2])[which(plotssurveyed[,3,2] == 0)])) 
c2014.ind5 <- cindex %>%
  filter(session == 2014 & time == 5 & Plot %in% as.numeric(names(plotssurveyed[,5,2])[which(plotssurveyed[,5,2] == 0)]))
c2014.ind6 <- cindex %>%
  filter(session == 2014 & time == 6 & Plot %in% as.numeric(names(plotssurveyed[,6,2])[which(plotssurveyed[,6,2] == 0)])) 
c2014.ind7 <- cindex %>%
  filter(session == 2014 & time == 7 & Plot %in% as.numeric(names(plotssurveyed[,7,2])[which(plotssurveyed[,7,2] == 0)])) 
c2014.ind8 <- cindex %>%
  filter(session == 2014 & time == 8 & Plot %in% as.numeric(names(plotssurveyed[,8,2])[which(plotssurveyed[,8,2] == 0)])) 
c2014.ind9 <- cindex %>%
  filter(session == 2014 & time == 9 & Plot %in% as.numeric(names(plotssurveyed[,9,2])[which(plotssurveyed[,9,2] == 0)])) 
c2014.ind10 <- cindex %>%
  filter(session == 2014 & time == 10 & Plot %in% as.numeric(names(plotssurveyed[,10,2])[which(plotssurveyed[,10,2] == 0)])) 
c2014.inds <- c(c2014.indices$par.index, c2014.ind1$par.index, c2014.ind2$par.index, c2014.ind3$par.index, c2014.ind5$par.index,
                c2014.ind6$par.index, c2014.ind7$par.index, c2014.ind8$par.index, c2014.ind9$par.index, c2014.ind10$par.index)


## Missed in 2015
c2015.indices <- cindex %>%
  filter(session == 2015 & time == 10) 
c2015.ind1 <- cindex %>%
  filter(session == 2015 & time == 1 & Plot %in% as.numeric(names(plotssurveyed[,1,3])[which(plotssurveyed[,1,3] == 0)])) 
c2015.ind2 <- cindex %>%
  filter(session == 2015 & time == 2 & Plot %in% as.numeric(names(plotssurveyed[,2,3])[which(plotssurveyed[,2,3] == 0)])) 
c2015.ind3 <- cindex %>%
  filter(session == 2015 & time == 3 & Plot %in% as.numeric(names(plotssurveyed[,3,3])[which(plotssurveyed[,3,3] == 0)]))
c2015.ind4 <- cindex %>%
  filter(session == 2015 & time == 4 & Plot %in% as.numeric(names(plotssurveyed[,4,3])[which(plotssurveyed[,4,3] == 0)]))
c2015.ind5 <- cindex %>%
  filter(session == 2015 & time == 5 & Plot %in% as.numeric(names(plotssurveyed[,5,3])[which(plotssurveyed[,5,3] == 0)])) 
c2015.ind6 <- cindex %>%
  filter(session == 2015 & time == 6 & Plot %in% as.numeric(names(plotssurveyed[,6,3])[which(plotssurveyed[,6,3] == 0)])) 
c2015.ind7 <- cindex %>%
  filter(session == 2015 & time == 7 & Plot %in% as.numeric(names(plotssurveyed[,7,3])[which(plotssurveyed[,7,3] == 0)])) 
c2015.ind8 <- cindex %>%
  filter(session == 2015 & time == 8 & Plot %in% as.numeric(names(plotssurveyed[,8,3])[which(plotssurveyed[,8,3] == 0)])) 
c2015.ind9 <- cindex %>%
  filter(session == 2015 & time == 9 & Plot %in% as.numeric(names(plotssurveyed[,9,3])[which(plotssurveyed[,9,3] == 0)])) 

c2015.inds <- c(c2015.indices$par.index, c2015.ind1$par.index, c2015.ind2$par.index, c2015.ind3$par.index, c2015.ind4$par.index,
                c2015.ind5$par.index, c2015.ind6$par.index, c2015.ind7$par.index, c2015.ind8$par.index, c2015.ind9$par.index)
## Final for all missed ones that need to be zero
c.indices <- c(c2013.inds,c2014.inds, c2015.inds)
c.values <- rep(0, length(c.indices))

Huggins <- mark(data = RDproc, ddl = RDddl, model = "CRDMSOHug",
                      time.intervals = time.intervals, begin.time = 2013)

Huggins$results$real %>%
  distinct(estimate, se, lcl, ucl)

HugginsRDclosedMSmodeldot <- mark(data = RDproc, ddl = RDddl, model = "CRDMSOHug",
                      time.intervals = time.intervals,
                      model.parameters = list(
                                              # S = list(formula = ~ stratum + Plot),
                                              # Psi = list(formula = ~ stratum + Plot),
                                              # Omega = list(formula = ~ stratum + Plot),
                                              S = list(formula = ~ stratum ),
                                              Psi = list(formula = ~ stratum ),
                                              Omega = list(formula = ~ stratum ),
                                              p = list(formula = ~ stratum, fixed = list(index = p.indices, value = p.values)),
                                              c = list(formula = ~ stratum, fixed = list(index = c.indices, value = c.values)))
                      )

head(summary(HugginsRDclosedMSmodeldot, show.fixed = TRUE))
HugginsRDclosedMSmodeldot$results$real %>%
  distinct(estimate, se, lcl, ucl)

plotSite <- obsmodel %>%
  distinct(Plot, Site) %>%
  dplyr::rename(plot = Plot) %>%
  mutate(plot = as.character(plot))

## Fixed to zero for times when not viewed
HugginsRDclosedMSmodeldot$results$real %>%
  mutate(dats = row.names(.)) %>%
  mutate(dats = gsub(" to", "to",dats)) %>%
  separate(dats, into = c("Parameter", "stage","plot")) %>%
  # mutate(plot = gsub("g","",plot)) %>%
  # mutate(plot = as.character(plot)) %>%
  # left_join(plotSite) %>%
  mutate(Parameter = as.factor(Parameter)) %>%
  # mutate(Parameter = factor(Parameter, levels = c("S","Phi","Omega","p","c"))) %>%
ggplot(  aes( estimate, Parameter,color = stage))+
  geom_point(position = position_dodge(width = 0.4)) +
  geom_errorbar(aes(xmin = lcl, xmax = ucl, width = 0.2),position = position_dodge(width = 0.4))+
  # geom_errorbar(aes(ymin = lcl, ymax = ucl, width = 0.1),position = position_dodge(width = 0.4))+
  theme_bw()+
  ylab("")+
  scale_color_manual("Stage", values = c("black","black","blue","blue"), 
                     labels = c("Reproductive", "R to V", "Vegetative", "V to R")) 
  # facet_wrap(~ Site)

Hugginstime <- mark(data = RDproc, ddl = RDddl, model = "CRDMSOHug",
                      time.intervals = time.intervals,
                      model.parameters = list(S = list(formula = ~ Plot),
                                              Psi = list(formula = ~ Plot),
                                              Omega = list(formula = ~ stratum),
                                              p = list(formula = ~ stratum, fixed = list(index = p.indices, value = p.values)),
                                              c = list(formula = ~ stratum, fixed = list(index = c.indices, value = c.values)))
                      )

head(summary(HugginsRDclosedMSmodeldot, show.fixed = TRUE))
HugginsRDclosedMSmodeldot$results$real %>%
  distinct(estimate, se, lcl, ucl)

## Ratio of juvenile to adult
0.5204678/0.8434238
  

HugginsRDclosedMSmodeldot$results$derived
```


```{r}

## To compare
## Average across two years
# matU <- mean(list(MPM.all$Plot1$Year2013$T,MPM.all$Plot1$Year2014$T))
# matF <- mean(list(MPM.all$Plot1$Year2013$F,MPM.all$Plot1$Year2014$F))
## To compare using the average across sites and years
matU <- mean(do.call(c, lapply(asmi.3yrs, function(x) lapply(x, function(y) y$T))))

##Survival
## dormant 0.8611111 because sometimes no dormant to start with, should get rid of zeros because need only measures of when there are some? or all die. That's true for vegetative and reproductive, that sometimes they may not be any, sometimes non-survive. 
apply(data.frame(do.call(c, lapply(asmi.3yrs, function(x) lapply(x, function(y) colSums(y$T))))),1,mean)
surv.nozeros <- data.frame(do.call(rbind,do.call(c, lapply(asmi.3yrs, function(x) lapply(x, function(y) colSums(y$T))))))
mean(surv.nozeros$dormant[surv.nozeros$dormant > 0])
mean(surv.nozeros$vegetative[surv.nozeros$vegetative > 0])
mean(surv.nozeros$reproductive[surv.nozeros$reproductive > 0])

matF <- mean(do.call(c, lapply(asmi.3yrs, function(x) lapply(x, function(y) y$F))))  

log(lambda(matU + matF))
lambda(matU + matF)
colSums(sensitivity(matU + matF))
el <- elasticity(matU + matF)
mx <- mpm_to_mx(matU, matF, lx_crit = 0.01)   # age from stage, age specific reproduction
lx <- mpm_to_lx(matU, lx_crit = 0.01) ## age from stage, age-specific survivorship
convShape <- shape_rep(mx)
convDegreeItero <- entropy_d(lx, mx) ## these are sensitive to length of vectors, and partial survivorship and fecundity - better to use shape_rep
gen_time(matU, matF, method = "R0")

## Vital rates are non-zero elements of A, elasticities
Adf <- data.frame(vr = as.vector(el), logvr = log2(as.vector(el)))
Adf <- Adf %>%
  mutate(plnp = vr*logvr)
Hprime <- -sum(Adf$plnp)
Hprimemax <- log2(nrow(Adf))
(EE <- Hprime/Hprimemax)

CH <- HugginsRDclosedMSmodeldot$results$real %>%
  distinct(estimate, se, lcl, ucl) %>%
  mutate(dats = row.names(.)) %>%
  mutate(dats = gsub(" to", "to",dats)) %>%
  mutate(dats = gsub(" a0", "", dats)) %>%
  mutate(dats = gsub(" a1", "", dats)) %>%
  mutate(dats = gsub(" a2", "", dats)) %>%
  separate(dats, into = c("Parameter", "stage")) %>% #, "plot", "year")) %>%
  mutate(stage = gsub("s", "",stage)) %>%
  mutate(ParameterStage = paste(Parameter, stage, sep = " ")) %>%
  filter(estimate != 0)

SV <- CH$estimate[CH$ParameterStage == "S V"]
GVR <- CH$estimate[CH$ParameterStage == "Psi VtoR"] 
SR <- CH$estimate[CH$ParameterStage == "S R"]
GRV <- CH$estimate[CH$ParameterStage == "Psi RtoV"]

## f from Pradel
load("data/PradelSBC.Rdata")

f <- asmi.models$Phi.dot.p.dot.f.dot$results$real$estimate[3]

matUMRC <- matrix(c(SV * (1-GVR), SV * GVR, (SR * GRV) + f, SR * (1-GRV) ),
                     nrow = 2)
lambda(matUMRC)
elasticity(matUMRC)
colSums(sensitivity(matUMRC))

colSums(matUMRC)
colSums(matU)

matU.MR <- matrix(c(SV * (1-GVR), SV * GVR, (SR * GRV), SR * (1-GRV) ),
                     nrow = 2)
matF.MR <- matrix(c(0, 0, f, 0 ),
                     nrow = 2)

lambda(matU.MR + matF.MR)
el.mr <- elasticity(matU.MR + matF.MR)
mx.mr <- mpm_to_mx(matU.MR, matF.MR, lx_crit = 0.01)   # age from stage, age specific reproduction
lx.mr <- mpm_to_lx(matU.MR, lx_crit = 0.01) ## age from stage, age-specific survivorship
convShape.mr <- shape_rep(mx.mr)
convDegreeItero <- entropy_d(lx.mr, mx.mr) ## these are sensitive to length of vectors, and partial survivorship and fecundity - better to use shape_rep
gen_time(matU.MR, matF.MR, method = "R0")

## Vital rates are non-zero elements of A, elasticities
Adf.mr <- data.frame(vr = as.vector(el.mr), logvr = log2(as.vector(el.mr)))
Adf.mr <- Adf.mr %>%
  mutate(plnp = vr*logvr)
Hprime.mr <- -sum(Adf.mr$plnp)
Hprimemax.mr <- log2(nrow(Adf.mr))
(EE <- Hprime.mr/Hprimemax.mr)

## survival is column sums. Transitions are the cell/survival
MPMparameters2 <- data.frame(estimate = c(colSums(matU)[1], colSums(matU)[2],
                                          matU[2,1]/colSums(matU)[1], matU[1,2]/colSums(matU)[2], 
                                         1, # colSums(matU)[3], ## Dormant is always 1. There are some transitions where there are no dormant
                                         matU[3,1]/colSums(matU)[1], matU[3,2]/colSums(matU)[2],  
                                         matU[1,3]/colSums(matU)[3], matU[2,3]/colSums(matU)[3]),
                            se = NA, lcl = NA, ucl = NA, 
                            Parameter = c("S","S",    "Psi","Psi",     "S", "Psi", "Psi", "Psi", "Psi"), 
                            stage =     c("V","R",  "VtoR","RtoV", "D", "VtoD", "RtoD", "DtoV", "DtoR"),
                            ParameterStage = c("S V", "S R", "Psi VtoR", "Psi RtoV", "S D", 
                                               "Psi VtoD", "Psi RtoD", "Psi DtoV", "Psi DtoR"),
                            Model = "Conventional")
                            



### Separate figures for survival, transitions, dormancy/detection, and reproduction
p2.v2 <- HugginsRDclosedMSmodeldot$results$real %>%
  distinct(estimate, se, lcl, ucl) %>%
  mutate(dats = row.names(.)) %>%
  mutate(dats = gsub(" to", "to",dats)) %>%
  mutate(dats = gsub(" a0", "", dats)) %>%
  mutate(dats = gsub(" a1", "", dats)) %>%
  mutate(dats = gsub(" a2", "", dats)) %>%
  separate(dats, into = c("Parameter", "stage")) %>% #, "plot", "year")) %>%
  mutate(stage = gsub("s", "",stage)) %>%
  mutate(ParameterStage = paste(Parameter, stage, sep = " ")) %>%
  filter(estimate != 0) %>%
  filter(Parameter != "Omega") %>%
  dplyr::select(c(estimate:ucl,Parameter:ParameterStage)) %>%
  mutate(Model = "Mark-recapture") %>%
  bind_rows(MPMparameters2) %>%
  mutate(ParameterStage = gsub("p ","first detection ", ParameterStage)) %>%
  mutate(ParameterStage = gsub( "c ","recapture ", ParameterStage)) %>%
  mutate(ParameterStage = factor(ParameterStage, levels = c("Psi RtoD","recapture R", 
                                                            "Psi VtoD","recapture V",
                                                            "first detection V","first detection R",
                                                            "Psi DtoR", "Psi DtoV", "Psi RtoV",
                                                            "Psi VtoR","S D", "S R", "S V"))) %>%
  mutate(stage1 = substr(stage, start = 1, stop = 1)) %>%
 ggplot(  aes(estimate, ParameterStage, color = stage1,
              shape = Model))+
  geom_point(position = position_dodge(width = 0.4), size = 2, stroke = 1.5) +
  geom_errorbar(aes(xmin = lcl, xmax = ucl, width = 0.5),position = position_dodge(width = 0.4))+
  theme_bw()+
  ylab("")+
  scale_color_manual("Stage", values = c("D" ="red","R" = "darkmagenta","V" = "darkseagreen"),
                     labels = c("Dormant","Reproductive","Vegetative"))+
  annotate("text", x = 0.2, y = 13, label = expression(paste("\u03A6", " survival")), size = 4, parse = TRUE)+
  geom_hline(yintercept = 10.5)+
  annotate("text", x= .67, y = 10, label = expression(paste("\u03C8"," stage transitions")), size = 4, parse=TRUE)+
  geom_hline(yintercept = 6.5)+
  annotate("text", x = 0.25, y = 6, label = expression(paste(italic("p"), " first detection")), size = 4, parse = TRUE)+
  geom_hline(yintercept = 4.5)+
  annotate("text", x = 0.25, y = 4, label = expression(paste(italic("c"), " & dormancy")), size = 4, parse = TRUE)+
  scale_y_discrete(labels = c("S V" = expression(S^"[Vegetative]"), "S R" = expression(S^"[Reproductive]"),
                              "S D" = expression(S^"[Dormant]"),
                              "Psi VtoR" = expression("\u03C8"^"[V,R]"), 
                              "Psi RtoV" = expression("\u03C8"^"[R,V]"),
                              "Psi DtoV" = expression("\u03C8"^"[D,V]"),
                              "Psi DtoR" = expression("\u03C8"^"[D,R]"),
                              "Psi VtoD" = expression("\u03C8"^"[V,D]"),
                              "Psi RtoD" = expression("\u03C8"^"[R,D]")) 
                   )+
  scale_shape_manual(values = c(4,20)) 


  
```



